Competence distance

### 2017-05-10 analysis/analysis_competence.Rmd
update competence analysis

```{r, warning=FALSE, message=FALSE}}
library("tidyverse")
```

@@

## Compute competence index

`TODO` documentar

```{r}
focal_trees <- compete %>% filter(id_core != 'Fresno') 
focal_trees <- unique(focal_trees$id_core)

output<- vector("list", length(focal_trees))

@@

# Create df   
df <- compete %>% 
  filter(id_core == focal_trees[[i]])

# Fixed Variables 
radius_plot <- 10 # radius plot (10 m)
sf_plot <- pi * radius_plot^2 # surface plot (m2)
dnft <- filter(df, sp== 'Focal')$dn # normal diameter focal tree    
# ----------

# Competence indices 
## Number of competitors (r = 10)
n_competitors <- filter(df, sp != 'Focal') %>% count()

@@

## Plot density (tree/plot)
plot_density <- n_competitors / sf_plot

@@

dist_nn <- (dist_nn$distance_cm / 100)

## Various 
### Basal area
### Size ratio proportional to distance 
### Size difference proportional to distance 
### Negative exponential size ratio
### Negative exponential weighted size ratio
### Lorimer 
### Crowding 
df_more_indices <- df %>%
  filter(sp != 'Focal') %>%
  mutate(
    basal_area = ((pi/4) * dn * dn), 
    size_ratio_distance = (dn / dnft) * (1 / ((distance_cm/100) + 1)),
    size_diff_distance = (dn - dnft) / ((distance_cm/100) + 1),
    neg_exp_size_ratio = (dn / dnft) * (1 / exp((distance_cm/100) + 1)),
    neg_exp_w_size_ratio = (dn / dnft) * exp((-(distance_cm/100) + 1) / (dn + dnft)),
    lorimer = (dn / dnft) / (sqrt((distance_cm/100) / radius_plot)),
    crowding = dn / (distance_cm/100))

df_indices <- df_more_indices %>% 
  summarise(ba = sum(basal_area),
            srd = sum(size_ratio_distance),
            sdd = sum(size_diff_distance),
            nesr = sum(neg_exp_size_ratio),
            newsr = sum(neg_exp_w_size_ratio),
            lorimer = sum(lorimer),
            crowding = sum(crowding)) %>% 
  mutate(nc = n_competitors,
         nch = n_competitors_hihger,
         pd = plot_density,
         std = stand_density,
         ss = sum_sizes,
         sr = size_ratio,
         dnn = dist_nn, 
         id_plot = focal_trees[[i]])

output[[i]] <- df_indices 
}

@@

rm(n_competitors, n_competitors_hihger, plot_density, stand_density, sum_sizes, size_ratio, dist_nn, df, df_indices, output, df_more_indices, dnft)
```

@@

```{r}
get_coords_trees <- function(angle, distance, x0, y0) {
  angle <- ifelse(angle <= 90, 90 - angle, 450 - angle)
  data.frame(x = x0 + distance * cos(angle / 180 * pi),
             y = y0+ distance * sin(angle / 180 * pi))
}

compete <- compete %>% 
  mutate(xcord = get_coords_trees(angle= rumbo_degree, 
                           distance = distance_cm/100,
                           x0 = 0, y0 = 0)$x,
         ycord = get_coords_trees(angle = rumbo_degree, 
                           distance = distance_cm/100,
                           x0 = 0, y0 = 0)$y)
```

```{r}
# see stackoverflow questions 6862742
gg_circle <- function(radius, xcenter, ycenter, color='black', fill=NA, ...){
  x <- xcenter + radius*cos(seq(0,pi, length.out = 100))
  ymax <- ycenter + radius*sin(seq(0, pi, length.out = 100))
  ymin <- ycenter + radius*sin(seq(0, -pi, length.out = 100))
  annotate("ribbon", x=x, ymin=ymin, ymax=ymax, color=color, fill=fill, ...)
}

compete %>%  
  filter(sp != 'Focal') %>%
  ggplot(aes(x=xcord, y=ycord)) + 
  facet_wrap(~id_core) + 
  geom_point(aes(size=perim_mm), shape=21, fill='transparent') + 
  xlim(-11,11) + ylim(-11,11) + 
  geom_point(aes(x=0, y=0), color='green') +
  theme_bw() +
  gg_circle(radius = 10, xcenter = 0, ycenter = 0) +
  theme(panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank()) 
```

>>>>

```{r, warning=FALSE, message=FALSE}}
library("tidyverse")
library("stringr")
```

@@

## Compute competence indexes

* Get unique identifier of focal tree 
* Competence indexes: 
    *

```{r}
# Get name of focal trees
focal_trees <- compete %>% filter(id_focal != 'Fresno') 
focal_trees <- unique(focal_trees$id_focal)

# Empty object to store results 
output<- vector("list", length(focal_trees))

@@

  # Create df with all trees inside plot (10 m radius)
  df <- compete %>% filter(id_focal == focal_trees[[i]])

  # Compute fixed variables: 
  radius_plot <- 10 # radius plot (10 m)
  sf_plot <- pi * radius_plot^2 # surface plot (m2)
  dnft <- filter(df, sp== 'Focal')$dn # normal diameter of focal tree    
  # ----------

  # Competence indices 
  ## Number of competitors inside plot wihtout focal tree (r = 10)
  n_competitors <- filter(df, sp != 'Focal') %>% count()

@@

  ## plot density (tree/plot)
  plot_density <- n_competitors / sf_plot

@@

  dist_nn <- (dist_nn$distance_cm / 100) #in meters

  ## Various 
  ### Basal area
  ### Size ratio proportional to distance 
  ### Size difference proportional to distance 
  ### Negative exponential size ratio
  ### Negative exponential weighted size ratio
  ### Lorimer 
  ### Crowding

  df_more_indices <- df %>%
    filter(sp != 'Focal') %>%
    mutate(basal_area = ((pi/4) * dn * dn), 
           size_ratio_distance = (dn / dnft) * (1 / ((distance_cm/100) + 1)),
           size_diff_distance = (dn - dnft) / ((distance_cm/100) + 1),
           neg_exp_size_ratio = (dn / dnft) * (1 / exp((distance_cm/100) + 1)),
           neg_exp_w_size_ratio = (dn / dnft) * exp((-(distance_cm/100) + 1) / (dn + dnft)),
           lorimer = (dn / dnft) / (sqrt((distance_cm/100) / radius_plot)),
           crowding = dn / (distance_cm/100))

  df_indices <- df_more_indices %>% 
    summarise(ba = sum(basal_area),
              srd = sum(size_ratio_distance),
              sdd = sum(size_diff_distance),
              nesr = sum(neg_exp_size_ratio),
              newsr = sum(neg_exp_w_size_ratio),
              lorimer = sum(lorimer),
              crowding = sum(crowding)) %>% 
    mutate(nc = n_competitors,
           nch = n_competitors_hihger,
           pd = plot_density,
           std = stand_density,
           ss = sum_sizes,
           sr = size_ratio,
           dnn = dist_nn,
           id_focal = focal_trees[[i]])

  output[[i]] <- df_indices

}

@@

rm(n_competitors, n_competitors_hihger, plot_density, stand_density, sum_sizes, size_ratio, dist_nn, df, df_indices, output, df_more_indices, dnft)

# Export data

@@

```{r}
source(paste0(getwd(), '/script/R/get_coords_trees.R'))

# Add variables with coordinates of each tree. Use get_coords_trees() function 
compete <- compete %>% 
  mutate(xcord = get_coords_trees(angle= rumbo_degree, 
                           distance = distance_cm/100,
                           x0 = 0, y0 = 0)$x,
         ycord = get_coords_trees(angle = rumbo_degree, 
                           distance = distance_cm/100,
                           x0 = 0, y0 = 0)$y)
```

## Plot by site 
```{r}
# Set levels of eleveation 
sj_lowcode  <- paste0('A', str_pad(1:10, 2, pad='0'))
sj_highcode <- paste0('A', 11:20)
ca_lowcode <- c(paste0('B', str_pad(1:10, 2, pad='0')),
            paste0('B', 26:30))
ca_highcode <- paste0('B', 11:25)

compete <- compete %>% 
  mutate(elev = ifelse(id_focal %in% sj_lowcode, 'Low',
                       ifelse(id_focal %in% sj_highcode, 'High',
                              ifelse(id_focal %in% ca_lowcode, 'Low', 'High')))) %>%
  mutate(site = paste0(loc, '_', elev))
```

# see stackoverflow questions 6862742
gg_circle <- function(radius, xcenter, ycenter, color='black', fill=NA, ...){
  x <- xcenter + radius*cos(seq(0,pi, length.out = 100))
  ymax <- ycenter + radius*sin(seq(0, pi, length.out = 100))
  ymin <- ycenter + radius*sin(seq(0, -pi, length.out = 100))
  annotate("ribbon", x=x, ymin=ymin, ymax=ymax, color=color, fill=fill, ...)
}
```

compete %>%  
  filter(sp != 'Focal') %>%
  ggplot(aes(x=xcord, y=ycord)) + 
  facet_wrap(~id_focal) + 
  geom_point(aes(size=perim_mm), shape=21, fill='transparent') + 
  xlim(-11,11) + ylim(-11,11) + 
  geom_point(aes(x=0, y=0), color='green') +
  theme_bw() +
  gg_circle(radius = 10, xcenter = 0, ycenter = 0) +
  theme(panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank()) 
```
